Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure - Supplementaty materials

### 2012-04-30 supplementary.tex
Changed supplemantry figure labels to S1, S2, etc...

\begin{document}
\section{Temperature dependence}
As mentioned in the main paper, the oscillations shows a very strong
temperature dependence. In Figure~\ref{fgr:temperature_dependence_supplemental}
we show an example where the oscillations are turned on and off by changing the
temperature $20^\circ$C.

@@

\subsection{Duty cycle}
Even though the period of the oscillations increases with time the total
integrated conversion rate during a complete cycle is almost constant. In
Figure~\ref{fgr:duty_cycles_supplemental} the mean value of CO and
CO$_2$ is plotted for every oscillation in a four-day long experiment. It is
evident that the ratio between CO and CO$_2$ is almost constant. The
average activity of the sample is thus almost unchanged despite the development in
the oscillation frequency.

>>>>

\renewcommand{\thefigure}{S\arabic{figure}}

\begin{document}
\section{Temperature dependence}
As mentioned in the main paper, the oscillations shows a very strong
temperature dependence. In \ref{fgr:temperature_dependence_supplemental}
we show an example where the oscillations are turned on and off by changing the
temperature $20^\circ$C.

@@

\subsection{Duty cycle}
Even though the period of the oscillations increases with time the total
integrated conversion rate during a complete cycle is almost constant. In
\ref{fgr:duty_cycles_supplemental} the mean value of CO and
CO$_2$ is plotted for every oscillation in a four-day long experiment. It is
evident that the ratio between CO and CO$_2$ is almost constant. The
average activity of the sample is thus almost unchanged despite the development in
the oscillation frequency.
